### 2023-11-18 ms.qmd
Updates

# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
data_associative <- data %>%
  group_by(lizard_id) %>%
    filter(sum(is.na(FC_associative)) <= 15) %>%
    filter(trial_associative <= 35) %>%
  ungroup()  %>% 
    mutate(temp = gsub("[AB]_", "", trt),
          cort = gsub("_[2][38]", "", trt))  %>% 
    mutate(group = factor(group, levels = c("R_B", "B_R"))) %>%
  data.frame()

# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)

data_associative <- data_associative %>%
  group_by(lizard_id) %>%
  mutate(
    first_non_na = min(which(!is.na(FC_associative))),
    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
    filter(Associative_Trial >= 1) %>%
   ungroup() %>% data.frame()

@@

@@

```{r, models2}
#| label: models2
#| echo: false
#| warning: false

@@

@@

# Plot delicata
plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial"),na.action = na.exclude) +
  facet_grid(as.factor(deli_associative$group)) + 
  labs(y = "Colour Association Task", x = "Trial")  
print(plot_deli)

# Plot guichenoti
plot_guich <- ggplot(guich_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial"),na.action = na.exclude) +
  facet_grid(as.factor(guich_associative$group)) + 
  labs(y = "Colour Association Task", x = "Trial") 
print(plot_guich)
```

>>>>

# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
data_associative <- data %>%
  group_by(lizard_id) %>%
    filter(sum(is.na(FC_associative)) <= 15) %>%
    filter(trial_associative <= 35) %>%
  ungroup()  %>% 
    mutate(temp = gsub("[AB]_", "", trt),
          cort = gsub("_[2][38]", "", trt))  %>% 
    mutate(group = factor(group,
     levels = c("R_B", "B_R"), 
     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
    mutate(temp = factor(temp,
     levels = c("23", "28"), 
     labels=c("23"="Cold", "28"="Hot"))) %>%
    mutate(cort = factor(cort,
     levels = c("A", "B"), 
     labels=c("A"="Control", "B"="CORT"))) %>%
  data.frame()

data_reversal <- data %>%
  group_by(lizard_id) %>%
    filter(sum(is.na(FC_reversal)) <= 15) %>%
   ungroup()  %>% 
    mutate(temp = gsub("[AB]_", "", trt),
          cort = gsub("_[2][38]", "", trt))  %>% 
    mutate(group = factor(group,
     levels = c("R_B", "B_R"), 
     labels=c("R_B"="Red", "B_R"="Blue"))) %>%
    mutate(temp = factor(temp,
     levels = c("23", "28"), 
     labels=c("23"="Cold", "28"="Hot"))) %>%
    mutate(cort = factor(cort,
     levels = c("A", "B"), 
     labels=c("A"="Control", "B"="CORT"))) %>%
  data.frame()

# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)
data_associative <- data_associative %>%
  group_by(lizard_id) %>%
  mutate(
    first_non_na = min(which(!is.na(FC_associative))),
    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
    filter(Associative_Trial >= 1) %>%
   ungroup() %>% data.frame()

@@

# Split data by species
deli_reversal <- data_reversal %>% filter (species == "delicata")
guich_reversal <- data_reversal %>% filter (species == "guichenoti")
```

@@

```{r, modelsasso}
#| label: modelsasso
#| echo: false
#| warning: false

@@

```{r, modelsrev}
#| label: modelsrev
#| echo: false
#| warning: false

# Bayesian model delicata
  deli_rev <- brm(FC_reversal ~ cort*temp*trial_reversal + group*trial_reversal + (1 + trial_reversal|lizard_id), data = deli_reversal, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(deli_rev)
  plot(deli_rev)

# Bayesian model guichenoti
  guich_rev <- brm(FC_reversal ~ cort*temp*trial_reversal + group*trial_reversal + (1 + trial_reversal|lizard_id), data = guich_reversal, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(guich_rev)
  plot(guich_rev)
# R2
bayes_R2(deli_rev)
bayes_R2(guich_rev)

@@

# Plot delicata associative
plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
  facet_grid(as.factor(deli_associative$group)) + 
  labs(y = "Probability of correct choice", x = "Trial")  
print(plot_deli)

# Plot guichenoti associative
plot_guich <- ggplot(guich_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial"),na.action = na.exclude) +
  facet_grid(as.factor(guich_associative$group)) + 
  labs(y = "Probability of correct choice", x = "Trial") 
print(plot_guich)

# Plot delicata reversal

# Plot guichenoti reversal
